**Density Dependence**

### 2023-03-07 Rmd/mseMac.Rmd
checked!

+  Load ICES assessment
+  Time varying M
+  Conduct VPA

@@

```{r, pars}
params=FLPar(c(m1=0.15/(0.2^-0.288),m2=-0.288,bref=NA,delta=-0.3,matk=30,w50=0.17))
```

@@

omFmsy=fwdWindow(window(iter(om,51),end=2020),end=2080,eqM)
F =propagate(fbar(omFmsy[,ac(2020:2080)]),4)
F[]=rep(rfpts$Fmsy,each=61)
control=as(FLQuants("f"=F),"fwdControl")

omFmsy =fwd(omFmsy,control=control,sr=eqM)

prj=FLStocks("Base"     =omFmsy)
prj[["DD Mass"]]        =omFmsy
prj[["DD Mass, Mat"]]   =omFmsy
prj[["DD Mass, Mat, M"]]=omFmsy
for (i in ac(2020:2080)) {
    prj[[2]] =ddFn(i,prj[[2]],params,massFlag=TRUE,matFlag=FALSE,mFlag=FALSE)
    control=as(FLQuants("f"=F[,i]),"fwdControl")
    prj[[2]] =fwd(prj[[2]],control=control,sr=eqM)

    prj[[3]] =ddFn(i,prj[[3]],params,massFlag=TRUE,matFlag=TRUE,mFlag=FALSE)
    control=as(FLQuants("f"=F[,i]),"fwdControl")
    prj[[3]] =fwd(prj[[3]],control=control,sr=eqM)

    prj[[4]] =ddFn(i,prj[[4]],params,massFlag=TRUE,matFlag=TRUE,mFlag=TRUE)
    control=as(FLQuants("f"=F[,i]),"fwdControl")
    prj[[4]] =fwd(prj[[4]],control=control,sr=eqM)
    }
```

```{r}
ts=ldply(prj, function(x) model.frame(FLQuants(x, ssb  =function(x) ssb(  x), 
                                                  f    =function(x) fbar(x), 
                                                  catch=function(x) catch(x)),drop=T))
ts=transform(ts,What=.id)
ts=transform(ts,.id=unique(eqCurves$.id)[an(iter)])

#plot(prj,probs=0,worm=seq(4))+facet_grid(qname~stock,scale="free")
```

```{r, check, fig.height=6,fig.width=8}
ggplot()+
  geom_line( aes(ssb,catch,col=.id),   data=eqCurves)+
  geom_point(aes(ssb,catch,col=.id),data=subset(ts,year==2040))+
  theme_bw()+theme(legend.position="bottom")+
  xlab("SSB")+ylab("Yield")
```

@@

    ## No DD ####################################################
    control=as(FLQuants("f"=F),"fwdControl")
    x1     =fwd(base,control=control,sr=eqM,residuals=devRec)

    ## With DD ####################################################
    x2=x1
    x3=x1
    x4=x1
    for (iYr in ac(2020:2080)) {
        control=as(FLQuants("f"=F[,iYr]),"fwdControl")

          ## DD M ##################################################         
          x2 =ddFn(iYr,x2,params,massFlag=TRUE,matFlag=FALSE,mFlag=FALSE)
          x2 =fwd(x2,control=control,sr=eqM,residuals=devRec)

          ## DD MM##################################################
          x3 =ddFn(iYr,x3,params,massFlag=TRUE,matFlag=TRUE,mFlag=FALSE)
          x3 =fwd(x3,control=control,sr=eqM,residuals=devRec)

          ## DD MMM ################################################
          x4 =ddFn(iYr,x4,params,massFlag=TRUE,matFlag=TRUE,mFlag=TRUE)
          x4 =fwd(x4,control=control,sr=eqM,residuals=devRec)
          }

@@

```{r}
om.  =om
oms. =oms
prj. =prj
prjs.=prjs   
save(eqM,    file="~/Desktop/tmp/eqM.RData")
save(om.,    file="~/Desktop/tmp/om..RData")
save(omFmsy, file="~/Desktop/tmp/omFmsy.RData")
save(oms.,   file="~/Desktop/tmp/oms..RData")
save(prj.,   file="~/Desktop/tmp/prj..RData")
save(prjs.,  file="~/Desktop/tmp/prjs..RData") 
```

@@

    ## No DD ####################################################
    control=as(FLQuants("f"=F),"fwdControl")
    x1     =fwd(iter(base,1),control=control,sr=eqM)

    ## With DD ####################################################
    x2=x1
    x3=x1
    x4=x1
    for (iYr in ac(2020:2080)) {
        control=as(FLQuants("f"=F[,iYr]),"fwdControl")

          ## DD M ##################################################         
          x2 =ddFn(iYr,x2,params,massFlag=TRUE,matFlag=FALSE,mFlag=FALSE)
          x2 =fwd(x2,control=control,sr=eqM)

          ## DD MM##################################################
          x3 =ddFn(iYr,x3,params,massFlag=TRUE,matFlag=TRUE,mFlag=FALSE)
          x3 =fwd(x3,control=control,sr=eqM)

          ## DD MMM ################################################
          x4 =ddFn(iYr,x4,params,massFlag=TRUE,matFlag=TRUE,mFlag=TRUE)
          x4 =fwd(x4,control=control,sr=eqM)
          }

@@

plot(vpaM_eq)
```

>>>>

-   Load ICES assessment
-   Time varying M
-   Conduct VPA

@@

```{r, pars}
params=FLPar(c(m1=0.15/(0.2^-0.288),m2=-0.288,   bref=3.69e+06,delta=-0.3,     matk=30,      w50=0.17))
params=FLPar(c(m1=9.69e-02         ,m2=-2.88e-01,bref=4.11e+06,delta=-2.00e-01,matk=2.80e+01,w50=1.66e-01)) 
```

@@

omFmsy=fwdWindow(window(iter(om,51),end=2020),end=2080,eqM)
F =propagate(fbar(omFmsy[,ac(2020:2080)]),4)
F[]=rep(rfpts$Fmsy,each=61)

omFmsy =fwd(omFmsy,fbar=F,sr=eqM)

prj=FLStocks("Base"     =omFmsy)
prj[["DD Mass"]]        =omFmsy
prj[["DD Mass, Mat"]]   =omFmsy
prj[["DD Mass, Mat, M"]]=omFmsy
for (i in ac(2020:2080)) {
    prj[[2]] =ddFn(i,prj[[2]],params,massFlag=TRUE,matFlag=FALSE,mFlag=FALSE)
    prj[[2]] =fwd(prj[[2]],fbar=F[,i],sr=eqM)

    prj[[3]] =ddFn(i,prj[[3]],params,massFlag=TRUE,matFlag=TRUE,mFlag=FALSE)
    prj[[3]] =fwd(prj[[3]],fbar=F[,i],sr=eqM)

    prj[[4]] =ddFn(i,prj[[4]],params,massFlag=TRUE,matFlag=TRUE,mFlag=TRUE)
    prj[[4]] =fwd(prj[[4]],fbar=F[,i],sr=eqM)
    }
```

```{r, check, fig.height=6,fig.width=8}
eqCurves=ldply(oms, function(x) { 
  model.frame(FLQuants(x[,dim(oms[[1]])[2]],
             biomass=function(x) stock(x),
             ssb    =function(x) ssb(  x),
             catch  =function(x) catch(x),
             f      =function(x) fbar( x)),drop=TRUE)[,-1]})

ts=ldply(prj, function(x) model.frame(FLQuants(x, ssb  =function(x) ssb(  x), 
                                                  f    =function(x) fbar(x), 
                                                  catch=function(x) catch(x)),drop=T))
ts=transform(ts,What=.id)
ts=transform(ts,.id=unique(eqCurves$.id)[an(iter)])

ggplot()+
  geom_line( aes(ssb,catch,col=.id),data=eqCurves)+
  geom_point(aes(ssb,catch,col=.id),data=subset(ts,year==2040))+
  theme_bw()+theme(legend.position="bottom")+
  xlab("SSB")+ylab("Yield")
```

@@

    ## No DD ####################################################
    x1     =fwd(base,fbar=F,sr=eqM,residuals=devRec)

    ## With DD ####################################################
    x2=x1
    x3=x1
    x4=x1
    for (iYr in ac(2020:2080)) {
          ## DD M ##################################################         
          x2 =ddFn(iYr,x2,params,massFlag=TRUE,matFlag=FALSE,mFlag=FALSE)
          x2 =fwd(x2,fbar=F[,iYr],sr=eqM,residuals=devRec)

          ## DD MM##################################################
          x3 =ddFn(iYr,x3,params,massFlag=TRUE,matFlag=TRUE,mFlag=FALSE)
          x3 =fwd(x3,fbar=F[,iYr],sr=eqM,residuals=devRec)

          ## DD MMM ################################################
          x4 =ddFn(iYr,x4,params,massFlag=TRUE,matFlag=TRUE,mFlag=TRUE)
          x4 =fwd(x4,fbar=F[,iYr],sr=eqM,residuals=devRec)
          }

@@

```{r}
om.  =om
oms. =oms
prj. =prj
prjs.=prjs   
save(eqM,    file="~/Desktop/tmp/eqM.RData")
save(om.,    file="~/Desktop/tmp/om..RData")
save(omFmsy, file="~/Desktop/tmp/omFmsy.RData")
save(oms.,   file="~/Desktop/tmp/oms..RData")
save(prj.,   file="~/Desktop/tmp/prj..RData")
save(prjs.,  file="~/Desktop/tmp/prjs..RData")
save(params, file="~/Desktop/tmp/params.RData") 
```

@@

    ## No DD ####################################################
    x1     =fwd(iter(base,1),fbar=F,sr=eqM)

    ## With DD ####################################################
    x2=x1
    x3=x1
    x4=x1
    for (iYr in ac(2020:2080)) {
          ## DD M ##################################################         
          x2 =ddFn(iYr,x2,params,massFlag=TRUE,matFlag=FALSE,mFlag=FALSE)
          x2 =fwd(x2,fbar=F[,iYr],sr=eqM)

          ## DD MM##################################################
          x3 =ddFn(iYr,x3,params,massFlag=TRUE,matFlag=TRUE,mFlag=FALSE)
          x3 =fwd(x3,fbar=F[,iYr],sr=eqM)

          ## DD MMM ################################################
          x4 =ddFn(iYr,x4,params,massFlag=TRUE,matFlag=TRUE,mFlag=TRUE)
          x4 =fwd(x4,fbar=F[,iYr],sr=eqM)
          }

@@

plot(FLStocks("MSE"=oms.[[2]],"Report"=oms[[2]]))

eqCurves=ldply(oms., function(x) { 
    model.frame(FLQuants(x[,dim(oms[[1]])[2]],
                         biomass=function(x) stock(x),
                         ssb    =function(x) ssb(  x),
                         catch  =function(x) catch(x),
                         f      =function(x) fbar( x)),drop=TRUE)[,-1]})
ts=ldply(prj., function(x) model.frame(FLQuants(x, ssb  =function(x) ssb(  x), 
                                                  f    =function(x) fbar(x), 
                                                  catch=function(x) catch(x)),drop=T))
ts=transform(ts,What=.id)
ts=transform(ts,.id=unique(eqCurves$.id)[an(iter)])

ggplot()+
    geom_line( aes(ssb,catch,col=.id),data=eqCurves)+
    geom_point(aes(ssb,catch,col=.id),data=subset(ts,year==2040))+
    theme_bw()+theme(legend.position="bottom")+
    xlab("SSB")+ylab("Yield")

eqCurves=ldply(oms, function(x) { 
    model.frame(FLQuants(x[,dim(oms[[1]])[2]],
                         biomass=function(x) stock(x),
                         ssb    =function(x) ssb(  x),
                         catch  =function(x) catch(x),
                         f      =function(x) fbar( x)),drop=TRUE)[,-1]})
ts=ldply(prj, function(x) model.frame(FLQuants(x, ssb  =function(x) ssb(  x), 
                                                  f    =function(x) fbar(x), 
                                                  catch=function(x) catch(x)),drop=T))
ts=transform(ts,What=.id)
ts=transform(ts,.id=unique(eqCurves$.id)[an(iter)])

ggplot()+
    geom_line( aes(ssb,catch,col=.id),data=eqCurves)+
    geom_point(aes(ssb,catch,col=.id),data=subset(ts,year==2040))+
    theme_bw()+theme(legend.position="bottom")+
    xlab("SSB")+ylab("Yield")
```
